Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-06-03 analysis/paper/shceof.Rmd
Cambia código para usar datos de zenodo finales

sams <- readRDS(data_path("derived", "sam.Rds")) %>%
  .[season(time) == "SON"] %>%
  .[, estimate := estimate*season_weights(time)] %>% 
  .[, .(estimate = mean(estimate)),
    by = .(lev, term, time = seasonally(time))]

>>>>

sams <- SAM() %>% 
  fread() %>%
  .[season(time) == "SON"] %>%
  .[, estimate := estimate*season_weights(time)] %>% 
  .[, .(estimate = mean(estimate)),
    by = .(lev, term, time = seasonally(time))]
